%basic cover letter template
\documentclass{letter}
\usepackage{amssymb,amsmath}
\usepackage{graphicx}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

\newcommand {\qed}{\mbox{$\Box$}}
\renewcommand {\iff}{\Longleftrightarrow}
\newcommand {\R}{\mathbb{R}}
\newcommand {\N}{\mathbb{N}}
\newcommand {\Q}{\mathbb{Q}}
\newcommand {\Z}{\mathbb{Z}}

\newcommand {\sub}{\mbox{SB}}

\begin{document}
\begin{letter}{\\
Reflex Traffic System Pty Ltd\\
31 Market Street, South Melbourne,\\
Victoria 3205, Australia}

\opening{Dear Sir or Madam,}
I am writing to apply for the position of C++ Software Engineeras. With five years plus experience in software development and Embedded system design, I see myself as an excellent fit for this role.

Through my career as a Software Enigneer, I have extensive experience in cross platform C++ Qt applications development and FreeRTOS embedded system design. In Blackmagic Design, my responsibilities includes developing new Application, enginnering tools(video/audio), API implemntation. My most recent project is implemntation of Video Asiist 4K 3D Lut feature. I am solely responsible for this project and the product's release cycle.

With an Electronics Enginnering and Physics background, I have strong understanding of product from system level and experience in hardware integration. In my first job at Welling \& Crossley, I involved in many electrical/electronics and control system projects, which requires integrating developed electronics modules or commertial sub components into a larger system where there are sensors, actuator, mechanical lever, engines, electric motors, generator, and VFD. As a lead engineer, I was aslo in charged of bringing a new product - AS2941 diesel fire pump control panel from concept to release. 

Beiing a software engineer, I always push myself to continuously deliver the highly efficient software and inovative solution. My interests, however, extend far beyond my work. I have been actively engaging in online courses including  
machine learning, Aerial Robotics from Coursera, and AI for Robotics from Udacity. They open a new way of thinking for me in solving real world problems. As an extension to the courses, I developed an opensource quadcopter 3D simulator, and self-driving robot-car simulator on GitHub, which also demostrates my competency in advanced mathematics and strong algorithm design ability in AI.     

I believe my versatile skill set, accompanied by various work and outside work experiences, could allow me to significantly contribute to your organisation. \textbf{SubjectLine} is \textbf{FPG}

\closing{Sincerely,}
Peter Huang\\
38 Miles Franklin Bvd\\
Point Cook, 3030 VIC\\
(+61) 430001790 \\hbd730@gmail.com\\

\end{letter}

\end{document}

